---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="man/figures/README-",
  out.width="100%"
)
options(tibble.print_min=5, tibble.print_max=5)
```

# vns: Verarbeitung Natürlicher Sprache

Welcome to the vns R package! vns stands for the German term "Verarbeitung Natürlicher Sprache," which translates to "Natural Language Processing" in English. This package is a collection of quantitative text analysis tools specifically designed with a focus on the German language.

## Installation

You can install the development version of vns from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("m-pilarski/vns")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(vns)
```

### Example Data Sets

```{r}
amazon_review_tbl <- load_amazon_review_tbl()

head(amazon_review_tbl)
```
