---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="man/figures/README-",
  out.width="100%"
)
options(tibble.print_min=5, tibble.print_max=5)
```

# vns: Verarbeitung Natürlicher Sprache

Welcome to the vns R package! vns stands for the German term "Verarbeitung Natürlicher Sprache," which translates to "Natural Language Processing" in English. This package provides a comprehensive suite of tools for quantitative text analysis, specifically tailored for the German language.

## Installation

You can install the development version of vns from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("m-pilarski/vns")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(vns)
```

### Example Data Sets

```{r}
amazon_review_tbl <- load_amazon_review_tbl()

amazon_review_tbl
```
```{r}
amazon_review_tbl |> 
  dplyr::slice_sample(n=1e3) |> 
  dplyr::pull(doc_text) |> 
  parse_doc_spacy()
```

```{r, eval=FALSE}
# summary(amazon_review_tbl$doc_label_num)
# 
# amazon_review_tbl |> 
#   dplyr::mutate(
#     doc_label_class = factor(
#       dplyr::case_when(
#         doc_label_num < 2 ~ 1L, doc_label_num == 2 ~ 2L, doc_label_num > 2 ~ 3L,
#         .default=NA_integer_
#       ),
#       levels=1L:3L, labels=c("neg", "neu", "pos")
#     )
#   ) |> 
#   rsample::initial_split(strata=doc_label_class) |> 
#   (\(.splits){
#     cross_val_tbl <<- rsample::training(.splits)
#     final_val_tbl <<- rsample::testing(.splits)
#   })()
# 
# cross_val_splits <- rsample::vfold_cv(cross_val_tbl, strata=doc_label_class)
# 
# tune::
# 
# cross_val_splits$splits[[1]]$data
```

